<link rel="stylesheet" href="/scripts/chessboard/css/chessboard-1.0.0.css">

<!-- <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/css/bootstrap.min.css"  -->
<!--       integrity="sha384-Gn5384xqQ1aoWXA+058RXPxPg6fy4IWvTNh0E263XmFcJlSAwiGgFAW/dAiS6JXm" crossorigin="anonymous"> -->
        
<script src="https://code.jquery.com/jquery-3.5.1.min.js"
        integrity="sha384-ZvpUoO/+PpLXR1lu4jmpXWu80pZlYUAfxl5NsBMWOEPSjUn/6Z/hRTt8+pR6L4N2"
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/popper.js@1.12.9/dist/umd/popper.min.js" i
        integrity="sha384-ApNbgh9B+Y1QKtv3Rn7W3mgPxhU9K/ScQsAP7hUibX39j7fakFPskvXusvfa0b4Q"
        crossorigin="anonymous"></script>

<script src="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/js/bootstrap.min.js"
        integrity="sha384-JZR6Spejh4U02d8jOt6vLEHfe/JQGiRRSQQxSfFWpi1MquVdAyjUar5+76PVCmYl"
        crossorigin="anonymous"></script>

<script src="/scripts/chessboard/js/chessboard-1.0.0.js"></script>

<!-- https://www.ichess.net/blog/the-scotch-opening-an-attacking-chess-opening-for-white/ -->
<!-- https://lichess.org/study/ogcSXNKv -->
<!-- https://en.wikipedia.org/wiki/Scotch_Game -->

# Petrov's Defense

```{r, file='scripts/R/r-setup.R'}
```

```{ojs, file='scripts/js/board-setup.js'}
```

```{r}
petrov <-
  add_game(
    title = "intro",
    moves = c("e4", "e5", "Nf3", "Nf6"),
    notation = TRUE
  ) |>
  add_game(
    title = "classical",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "d6", "Nf3", "Nxe4"),
    start = 5,
    variations = c("classical-5d4", "classical-5Nc3", "classical-5Bf5")
  ) |>
  add_variation(
    title = "classical-5d4",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "d6", "Nf3", "Nxe4", "d4", "d5", "Bd3"),
    start = 9 
  ) |>
  add_variation(
    title = "classical-5Nc3",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "d6", "Nf3", "Nxe4", "Nc3", "Nxc3", "dxc3"),
    start = 9 
  ) |>
  add_variation(
    title = "classical-5Bf5",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "d6", "Nf3", "Nxe4", "Nc3", "Bf5", "Qe2"),
    start = 10 
  ) |>
  add_game(
    title = "damiano",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5", "Nxe4", "Qe2"),
    start = 6,
    variations = c("damiano-4Nf6", "damiano-4d5", "damiano-4Qe7")
  ) |>
  add_variation(
    title = "damiano-4Nf6",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5", "Nxe4", "Qe2",
              "Nf6", "Nc6+"),
    start = 8 
  ) |>
  add_variation(
    title = "damiano-4d5",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5", "Nxe4", "Qe2",
              "d5", "d3", "Qe7", "dxe4", "Qxe5", "exd5"),
    start = 8 
  ) |>
  add_variation(
    title = "damiano-4Qe7",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5", "Nxe4", "Qe2",
              "Qe7", "Qxe4", "d6", "d4", "dxe5", "dxe5", "Nc6", "Nc3"),
    start = 8 
  ) |>
  add_game(
    title = "stafford",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2"),
    start = 6,
    variations = c("stafford-6h5", "stafford-6Ng4", "stafford-9Qh5", "stafford-11Bxc2", "stafford-12Bxc2")
  ) |>
  add_variation(
    title = "stafford-6h5",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2",
              "h5", "c3", "Ng4", "d4", "Bd6", "e5+"),
    start = 12 
  ) |>
  add_variation(
    title = "stafford-6Ng4",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2",
              "Ng4", "Bxg4", "Qh4", "Qf3", "Bxg4", "Qg3", "Qxg3", "hxg3"),
    start = 12 
  ) |>
  add_variation(
    title = "stafford-9Qh5",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2",
              "Ng4", "Bxg4", "Qh4", "Qf3", "Bxg4", "Qg3",
              "Qh5", "h3", "Bd1", "Nc3", "Bb4", "Bd2", "Bxc3", "Rxd1", "Bxb2", "Qxc7"),
    start = 18 
  ) |>
  add_variation(
    title = "stafford-11Bxc2",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2",
              "Ng4", "Bxg4", "Qh4", "Qf3", "Bxg4", "Qg3",
              "Qh5", "h3", "Bd1", "Nc3", 
              "Bxc2", "Kd2"),
    start = 22 
  ) |>
  add_variation(
    title = "stafford-12Bxc2",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Nc6", "Nxc6", "dxc6", "d3", "Bc5", "Be2",
              "Ng4", "Bxg4", "Qh4", "Qf3", "Bxg4", "Qg3",
              "Qh5", "h3", "Bd1", "Nc3", "Bb4", "Bd2", 
              "Bxc2", "Rc1"),
    start = 24
  ) |>
  add_game(
    title = "other",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5"),
    start = 6,
    variations = c("other-3Qe7")
  ) |>
  add_variation(
    title = "other-3Qe7",
    moves = c("e4", "e5", "Nf3", "Nf6", "Nxe5",
              "Qe7", "d4", "d6", "Nf3", "Qxe4+", "Be2"),
    start = 6 
  ) |>
  clean_chess_df() |>
  write_png("Petrov")

ojs_define(petrov_t = petrov)
```

```{ojs}
petrov = transpose(petrov_t)
```

```{ojs}
petrov.filter(d => d.type === 'main')
  .map(d => board_setup(petrov, d.title))
```

## Introduction

Petrov's Defense begins with 1.e4 e5 2.Nf3 Nf6.
White has two main options for their third move:
3.Nxe5, the Classical Variation and 3.d4, the Steinitz Variation---here I focus on 3.Nxe5

```{r}
#| output: asis
put_board("intro")
```

## Classical Variation (3.Nxe5 d6)

3...d6 is Black's best response to 3.Nxe5, followed with 4.Nf3 Nxe4

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("classical")
# pgn_to_vec("d5 5.d3 Qe7 6.dxe4 Qxe5 7.exd5")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* White's typical response is <span class="variation" id="classical-5d4"> 5.d4 </span>, white is looking to kick Black's advanced knight from e4 with moves like c4 and Re1
* An alternative option for white is <span class="variation" id = "classical-5Nc3"> 5.Nc3 </span>, looking for Be3, Qd2, and 0-0-0 with a kingside attack
  * If <span class="variation" id="classical-5Bf5"> 5...Bf5 </span>, Black loses a piece
:::

::::


## The Damiano Defense (3.Nxe5 Nxe4)

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("damiano")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* 3...Nxe4 is bad for Black, 4.Qe2 poses quite a problem.
  * <span class ="variation" id="damiano-4Nf6"> 4...Nf6 </span> loses the queen
  * <span class ="variation" id="damiano-4d5"> 4...d5 </span> loses a pawn
  * <span class ="variation" id="damiano-4Qe7"> 4...Qe7 </span> is "best"
:::

::::



<!-- - 4...Nf6 5.Nc6+ wins the queen -->
<!-- - 4...d5 5.d3 Qe7 6.dxe4 Qxe5 7.exd5 loses a pawn -->
<!-- - 4...Qe7 5.Qxe4 d6 6.d4 dxe5 7.dxe5 Nc6 8.Nc3 is "best" -->

## Stafford Gambit (3.Nxe5 Nc6)

3...Nc6 is the dubious but tricky Stafford Gambit.
Once refuted, White has the advantage.
The key initial moves for white are 5.d3 (defending e4) followed by 6.Be2 (developing the bishop while defending against Ng4).

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("stafford")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* At this point, Black has two options:
  * If <span class="variation" id="stafford-6h5"> 6...h5 </span>, calmly kick the bishop 
  * If <span class="variation" id="stafford-6Ng4"> 6...Ng4 </span>, take the knight with 7.Bxg4 then defend with the queen

* In the latter, a queen trade is almost forced---Black may avoid this with <span class="variation" id="stafford-9Qh5"> 9...Qh5 </span>
  * This is tricky though, <span class="variation" id="stafford-11Bxc2"> 11...Bxc2 </span> and <span class="variation" id="stafford-12Bxc2"> 12...Bxc2 </span> are both bad ideas
:::

::::

<!-- https://lichess.org/study/dcgcdxrS -->

## Other responses to 3.Nxe5

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("other")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* <span class="variation" id="other-3Qe7"> 3...Qe7 </span> is mildly worse for Black
:::

::::

## References {.unnumbered}

<button class="btn" style="width: unset;">
<a href="pgn-files/Scotch.pgn" download="Petrov.pgn">
<i class="fa fa-download"></i> Download PGN
</a>
</button>






