<link rel="stylesheet" href="/scripts/chessboard/css/chessboard-1.0.0.css">

<!-- <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/css/bootstrap.min.css"  -->
<!--       integrity="sha384-Gn5384xqQ1aoWXA+058RXPxPg6fy4IWvTNh0E263XmFcJlSAwiGgFAW/dAiS6JXm" crossorigin="anonymous"> -->
        
<script src="https://code.jquery.com/jquery-3.5.1.min.js"
        integrity="sha384-ZvpUoO/+PpLXR1lu4jmpXWu80pZlYUAfxl5NsBMWOEPSjUn/6Z/hRTt8+pR6L4N2"
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/popper.js@1.12.9/dist/umd/popper.min.js" i
        integrity="sha384-ApNbgh9B+Y1QKtv3Rn7W3mgPxhU9K/ScQsAP7hUibX39j7fakFPskvXusvfa0b4Q" 
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/js/bootstrap.min.js" 
        integrity="sha384-JZR6Spejh4U02d8jOt6vLEHfe/JQGiRRSQQxSfFWpi1MquVdAyjUar5+76PVCmYl" 
        crossorigin="anonymous"></script>

<script src="/scripts/chessboard/js/chessboard-1.0.0.js"></script>

# Scandinavian Defense

```{r, file='scripts/R/r-setup.R'}
```

```{ojs, file='scripts/js/board-setup.js'}
```

```{r}
scandi <-
  add_game(
    title = "intro",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8"),
    orientation = "black",
    notation = TRUE
  ) |>
  add_game(
    title = "4d4_Nf6_5Nf3_Bg4",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4"),
    start = 7,
    orientation = "black",
    variations = c("v-4Nc3_Qd8_5Nf3_Bg4_6Bc4", "v-4Nc3_Qd8_5Nf3_Bg4_6Be2")
  ) |>
  add_variation(
    title = "v-4Nc3_Qd8_5Nf3_Bg4_6Bc4",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4",
              "Bc4", "e6", "h3", "Bxf3", "Qxf3", "c6", "Ne2", "Nbd7",  "O-O", "Bd6", "b3", "O-O", "Bb2", "a5"),
    start = 11 
  ) |>
  add_variation(
    title = "v-4Nc3_Qd8_5Nf3_Bg4_6Be2",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4",
              "Be2", "e6", "h3", "Bxf3", "Bxf3", "c6", "O-O", "Bd6",  "Ne2", "Nbd7", "c4", "O-O", "Nc3", "Qc7", "b3", "Rad8", "Bb2",  "Rfe8"),
    start = 11
  ) |>
  add_game(
    title = "2Nc3",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5"),
    orientation = "black",
    start = 3,
    variations = c("v-2Nc3-transpose", "v-2Nc3-4Qf3", "v-2Nc3-4Nd3", "v-2Nc3-4Nd3-9Nxe5", "v-2Nc3-4d3")
  ) |>
  add_variation(
    title = "v-2Nc3-transpose",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5", 
              "Nc3", "Qd8"),
    start = 7
  ) |>
  add_variation(
    title = "v-2Nc3-4Qf3",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5", 
              "Qf3", "Nc6", "Ne2", "f5", "Ng5", "Qxf3", "Nxf3", "e5", "d4", "e4", "Ne5", "Nge7"),
    start = 7
  ) |>
  add_variation(
    title = "v-2Nc3-4Nd3",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5", 
              "Ng3", "Nc6", "Nf3", "e5", "b3", "Be6", "Bb2", "O-O-O", "Bc4", "Qd7"),
    start = 7
  ) |>
  add_variation(
    title = "v-2Nc3-4Nd3-9Nxe5",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5", 
              "Ng3", "Nc6", "Nf3", "e5", "b3", "Be6", "Bb2", "O-O-O", "Bc4", "Qd7",
              "Nxe5", "Nxe5", "Bxe5", "Bxc4", "bxc4", "Re8", "f4", "f6"),
    start = 17
  ) |>
  add_variation(
    title = "v-2Nc3-4d3",
    moves = c("e4", "d5", "Nc3", "dxe4", "Nxe4", "Qd5", 
              "d3", "Nc6"),
    start = 7
  ) |>
  add_game(
    title = "2d4",
    moves = c("e4", "d5", "d4", "dxe4"),
    orientation = "black",
    start = 3
  ) |>
  add_game(
    title = "2d3",
    moves = c("e4", "d5", "d3", "dxe4", "dxe4", "Qxd1+", "Kxd1"),
    orientation = "black",
    start = 3
  ) |>
  clean_chess_df() |>
  write_png("Scandinavian-Defense")

ojs_define(scandi_t = scandi)
```

```{ojs}
transpose(scandi_t).filter(d => d.type === 'main')
  .map(d => board_setup(transpose(scandi_t), d.title))
```

## Introduction

The Scandinavian Defense begins with 1.e4 d5.
Then, white typically captures 2.exd5 and black recaptures with 2...Qxd5.
Here we will mainly be looking at at lines following 3.Nc3 Qd8,
although there are other options after 3.Nc3 (3...Qa5, 3...Qd6).

```{r}
#| output: asis
put_board("intro")
```

## Main Line (2.exd5 Qxd5)

### 4.d4 Nf6 

#### 5.Nf3 Bg4

5.Nf3 is the most common response to 4.d4 Nf6.
Meet this with 5...Bg4 to put pressure on d4 with the queen.
  
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("4d4_Nf6_5Nf3_Bg4")
```

<!-- <button class="btn btn-primary" type="button" data-toggle="collapse" data-target="#collapseExample" aria-expanded="false" aria-controls="collapseExample"> -->
<!-- <i class="fa-regular fa-file-lines"></i> -->
<!-- </button> -->


:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
  * <span class="variation" id = "v-4Nc3_Qd8_5Nf3_Bg4_6Bc4"> 6.Bc4 </span> threatens 7.Bxf7+ then 8.Ne5+
  * <span class="variation" id = "v-4Nc3_Qd8_5Nf3_Bg4_6Be2"> 6.Be2 </span> placeholder
:::

::::


<!-- <div class="collapse column-margin" id="collapseExample"> -->
<!--   <div class="card card-body"> -->
<!--     Anim pariatur cliche reprehenderit, enim eiusmod high life accusamus terry richardson ad squid. Nihil anim keffiyeh helvetica, craft beer labore wes anderson cred nesciunt sapiente ea proident. -->
<!--   </div> -->
<!-- </div> -->

#### 5.Bc4 a6

## What if <span style="text-decoration: line-through;">2exd4</span>?

### 2.Nc3 dxe4 3.Nxe4 Qd5

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("2Nc3")
```

:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
  * <span class="variation" id = "v-2Nc3-transpose"> 4.Nf6 Qd8 </span> transposes back to the mainline
  * Instead of retreating, white might protect the knight with <span class="variation" id = "v-2Nc3-4Qf3"> 4.Qf4 </span>
  * <span class="variation" id = "v-2Nc3-4Nd3"> 4.Nd3 </span> is also an option 
  (note, black wins a piece if <span class="variation" id = "v-2Nc3-4Nd3-9Nxe5">9.Nxe5</span>)
  * <span class="variation" id = "v-2Nc3-4d3"> 4.d3 </span> is also an option, now black is looking for ...e7-e5
:::

::::

### 2. d4 (The Blackmar-Diemer Gambit)

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("2d4")
```

:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
  * temp
:::

::::



### 2. d3

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("2d3")
```

:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
  * The best response to 2. d3 is trading queens, entering a middle-game in which
  white can not castle
:::

::::


## References {.unnumbered}

<button class="btn" style="width: unset;">
<a href="pgn-files/Scandinavian-Defense.pgn" download="Scandinavian-Defense.pgn">
<i class="fa fa-download"></i> Download PGN
</a>
</button>


<!-- todo: -->
<!--   - 3...d6 -->
<!--   - 4...Nxd4 -->
<!--   - Göring Gambit -->





