<link rel="stylesheet" href="/scripts/chessboard/css/chessboard-1.0.0.css">

<!-- <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/css/bootstrap.min.css"  -->
<!--       integrity="sha384-Gn5384xqQ1aoWXA+058RXPxPg6fy4IWvTNh0E263XmFcJlSAwiGgFAW/dAiS6JXm" crossorigin="anonymous"> -->
        
<script src="https://code.jquery.com/jquery-3.5.1.min.js"
        integrity="sha384-ZvpUoO/+PpLXR1lu4jmpXWu80pZlYUAfxl5NsBMWOEPSjUn/6Z/hRTt8+pR6L4N2"
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/popper.js@1.12.9/dist/umd/popper.min.js" i
        integrity="sha384-ApNbgh9B+Y1QKtv3Rn7W3mgPxhU9K/ScQsAP7hUibX39j7fakFPskvXusvfa0b4Q" 
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/js/bootstrap.min.js" 
        integrity="sha384-JZR6Spejh4U02d8jOt6vLEHfe/JQGiRRSQQxSfFWpi1MquVdAyjUar5+76PVCmYl" 
        crossorigin="anonymous"></script>

<script src="/scripts/chessboard/js/chessboard-1.0.0.js"></script>

# Scandinavian Defense

```{r, file='scripts/R/r-setup.R'}
```

```{ojs, file='scripts/js/board-setup.js'}
```

```{r}
scandi <-
  add_game(
    title = "intro",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8"),
    orientation = "black",
    notation = TRUE
  ) |>
  add_game(
    title = "4d4_Nf6_5Nf3_Bg4",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4"),
    start = 7,
    orientation = "black",
    variations = c("v-4Nc3_Qd8_5Nf3_Bg4_6Bc4", "v-4Nc3_Qd8_5Nf3_Bg4_6Be2")
  ) |>
  add_variation(
    title = "v-4Nc3_Qd8_5Nf3_Bg4_6Bc4",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4",
              "Bc4", "e6", "h3", "Bxf3", "Qxf3", "c6", "Ne2", "Nbd7",  "O-O", "Bd6", "b3", "O-O", "Bb2", "a5"),
    start = 11 
  ) |>
  add_variation(
    title = "v-4Nc3_Qd8_5Nf3_Bg4_6Be2",
    moves = c("e4", "d5", "exd5", "Qxd5", "Nc3", "Qd8",
              "d4", "Nf6", "Nf3",  "Bg4",
              "Be2", "e6", "h3", "Bxf3", "Bxf3", "c6", "O-O", "Bd6",  "Ne2", "Nbd7", "c4", "O-O", "Nc3", "Qc7", "b3", "Rad8", "Bb2",  "Rfe8"),
    start = 11
  ) |>
  clean_chess_df() |>
  write_png("Scandinavian-Defense")

ojs_define(scandi_t = scandi)
```

```{ojs}
transpose(scandi_t).filter(d => d.type === 'main')
  .map(d => board_setup(transpose(scandi_t), d.title))
```

## Introduction

The Scandinavian Defense begins with 1.e4 d5.
Then, white typically captures 2.exd5 and black recaptures with 2...Qxd5.
Here, we will mainly be looking at at lines following 3.Nc3 Qd8.
While there are other options after 3.Nc3 (3...Qa5, 3...Qd6), I am focusing on 3...Qd8 for now.

```{r}
#| output: asis
put_board("intro")
```

## Main Line (2.exd5 Qxd5)

### 4.d4 Nf6 

#### 5.Nf3 Bg4

5.Nf3 is the most common response to 4.d4 Nf6.
Meet this with 5...Bg4 to put pressure on d4 with the queen.
  
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("4d4_Nf6_5Nf3_Bg4")
# put_board("classical")
```

<!-- <button class="btn btn-primary" type="button" data-toggle="collapse" data-target="#collapseExample" aria-expanded="false" aria-controls="collapseExample"> -->
<!-- <i class="fa-regular fa-file-lines"></i> -->
<!-- </button> -->


:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
  * <span class="variation" id = "v-4Nc3_Qd8_5Nf3_Bg4_6Bc4"> 6.Bc4 </span> threatens 7.Bxf7+ then 8.Ne5+
  * <span class="variation" id = "v-4Nc3_Qd8_5Nf3_Bg4_6Be2"> 6.Be2 </span> placeholder
:::

::::


<!-- <div class="collapse column-margin" id="collapseExample"> -->
<!--   <div class="card card-body"> -->
<!--     Anim pariatur cliche reprehenderit, enim eiusmod high life accusamus terry richardson ad squid. Nihil anim keffiyeh helvetica, craft beer labore wes anderson cred nesciunt sapiente ea proident. -->
<!--   </div> -->
<!-- </div> -->

#### 5.Bc4 a6


## References {.unnumbered}

<button class="btn" style="width: unset;">
<a href="pgn-files/Scandinavian-Defense.pgn" download="Scandinavian-Defense.pgn">
<i class="fa fa-download"></i> Download PGN
</a>
</button>


<!-- todo: -->
<!--   - 3...d6 -->
<!--   - 4...Nxd4 -->
<!--   - Göring Gambit -->





