<link rel="stylesheet" href="/scripts/chessboard/css/chessboard-1.0.0.css">

<!-- <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/css/bootstrap.min.css"  -->
<!--       integrity="sha384-Gn5384xqQ1aoWXA+058RXPxPg6fy4IWvTNh0E263XmFcJlSAwiGgFAW/dAiS6JXm" crossorigin="anonymous"> -->
        
<script src="https://code.jquery.com/jquery-3.5.1.min.js"
        integrity="sha384-ZvpUoO/+PpLXR1lu4jmpXWu80pZlYUAfxl5NsBMWOEPSjUn/6Z/hRTt8+pR6L4N2"
        crossorigin="anonymous"></script>
        
<script src="https://cdn.jsdelivr.net/npm/popper.js@1.12.9/dist/umd/popper.min.js" i
        integrity="sha384-ApNbgh9B+Y1QKtv3Rn7W3mgPxhU9K/ScQsAP7hUibX39j7fakFPskvXusvfa0b4Q"
        crossorigin="anonymous"></script>

<script src="https://cdn.jsdelivr.net/npm/bootstrap@4.0.0/dist/js/bootstrap.min.js"
        integrity="sha384-JZR6Spejh4U02d8jOt6vLEHfe/JQGiRRSQQxSfFWpi1MquVdAyjUar5+76PVCmYl"
        crossorigin="anonymous"></script>

<script src="/scripts/chessboard/js/chessboard-1.0.0.js"></script>

<!-- https://www.ichess.net/blog/the-scotch-opening-an-attacking-chess-opening-for-white/ -->
<!-- https://lichess.org/study/ogcSXNKv -->
<!-- https://en.wikipedia.org/wiki/Scotch_Game -->

# The Scotch

```{r, file='scripts/R/r-setup.R'}
```

```{ojs, file='scripts/js/board-setup.js'}
```

```{r}
scotch <-
  add_game(
    title = "intro",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4"),
    notation = TRUE
  ) |>
  add_game(
    title = "classical",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5"),
    start = 7,
    variations = c("classical-5Be3-7Bc4-O-O", "classical-5Be3-7Bc4-Ne5", "classical-5Nb3", "classical-5Nxc6")
  ) |>
  add_variation(
    title = "classical-5Be3-7Bc4-O-O",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5",
              "Be3", "Qf6", "c3", "Nge7", "Bc4", "0-0", "0-0", "Bb6"),
    start = 9
  ) |>
  add_variation(
    title = "classical-5Be3-7Bc4-Ne5",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5",
              "Be3", "Qf6", "c3", "Nge7", "Bc4", 
              "Ne5", "Be2", "Qg6", "O-O", "d6", "f3"),
    start = 14
  ) |>
  add_variation(
    title = "classical-5Nb3",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5",
              "Nb3", "Bb6", "a4", "a6", "Nc3"),
    start = 9
  ) |>
  add_variation(
    title = "classical-5Nxc6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5",
              "Nxc6", "Qf6", "Qd2", "dxc6", "Nc3"),
    start = 9
  ) |>
  add_game(
    title = "Schmidt",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nf6"),
    start = 7,
    variations = c("four-knights", "four-knights-5Nc3-Bc5", "Mieses")
  ) |>
  add_variation(
    title = "four-knights",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nf6",
              "Nc3", "Bb4", "Nxc6", "bxc6", "Bd3", "d5", "exd5", "cxd5", "0-0", "0-0", "Bg5", "c6", "Qf3"),
    start = 9
  )  |>
  add_variation(
    title = "four-knights-5Nc3-Bc5",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nf6",
              "Nc3", "Bc5", "Nxc6", "bxc6", "Bd3", "d6", "O-O", "Ng4", "h3"),
    start = 10
  )  |>
  add_variation(
    title = "Mieses",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nf6",
              "Nxc6", "bxc6", "e5", "Qe7", "Qe2", "Nd5", "c4"),
    start = 9
  ) |>
  add_game(
    title = "Knight-takes",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4"),
    start = 8,
    variations = c("Knight-takes-Nf6-Ng8", "Knight-takes-Nf6-Nh5", "Knight-takes-Nf6-c5", 
                   "Knight-takes-c5-d5", "Knight-takes-c5-d6",
                    "Knight-takes-Qf6", "Knight-takes-Qf6-8f6", "Knight-takes-Qf6-9Bxd6")
  ) |>
  add_variation(
    title = "Knight-takes-Nf6-Nh5",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Nf6", "e5", "Nh5", "g4", "c5", "Qd5", "d6", "gxh5"),
    start = 12
  ) |>
  add_variation(
    title = "Knight-takes-Nf6-Ng8",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Nf6", "e5", "Ng8", "Nc3", "b6", "Bf4", "Bc5", "Qd3", "Bb7", "O-O-O"),
    start = 12
  ) |>
  add_variation(
    title = "Knight-takes-Nf6-c5",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Nf6", "e5", "c5", "Qe3", "Nd5", "Qe4", "Nc7"),
    start = 12
  ) |>
  add_variation(
    title = "Knight-takes-c5-d5",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "c5", "Qd3", "d5", "Qxd5", "Qxd5", "exd5"),
    start = 10
  )  |>
  add_variation(
    title = "Knight-takes-c5-d6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "c5", "Qd3", "d6", "Nc3", "Nf6", "Bf4"),
    start = 12
  ) |>
  add_variation(
    title = "Knight-takes-Qf6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Qf6", "e5", "Qb6", "Qxb6", "axb6", "Bf4", "d6", "exd6", "cxd6"),
    start = 10
  ) |>
  add_variation(
    title = "Knight-takes-Qf6-8f6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Qf6", "e5", "Qb6", "Qxb6", "axb6", "Bf4", "f6", "exf6", 
              "Nxf6", "Bxc7"),
    start = 16
  ) |>
  add_variation(
    title = "Knight-takes-Qf6-9Bxd6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Nxd4", "Qxd4",
              "Qf6", "e5", "Qb6", "Qxb6", "axb6", "Bf4", "d6", "exd6", 
              "Bxd6", "Bxd6", "cxd6", "Nc3", "Nf6", "O-O-O", "d5", "Nxd5"),
    start = 18
  ) |>
  add_game(
    title = "Other-4",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4"),
    start = 8,
    variations = c("Other-4Nxd4-Qh4", "Other-4Nxd4-Qf6", "Other-4Nxd4-Bb4")
  ) |>
  add_variation(
    title = "Other-4Nxd4-Qh4",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4",
              "Qh4", "Nc3", "Bb4", "Be2", "Qxe4", "Nb5", "Bxc3+", "bxc3", "Kd8", "0-0"),
    start = 8
  ) |>
  add_variation(
    title = "Other-4Nxd4-Qf6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4",
              "Qf6", "Be3", "Bc5"),
    start = 8
  ) |>
  add_variation(
    title = "Other-4Nxd4-Bb4",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4",
              "Bb4", "c3", "Bc5", "Be3", "Bb6"),
    start = 8
  ) |>
  add_game(
    title = "scotch-gambit",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Bc4"),
    variations = c("scotch-gambit-variation-italian", "scotch-gambit-variation-accepted", "scotch-gambit-variation-london"),
    start = 7
  ) |>
  add_variation(
    title = "scotch-gambit-variation-italian",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Bc4",
              "Bc5", "c3", "Nf6"),
    start = 8
  ) |>
  add_variation(
    title = "scotch-gambit-variation-accepted",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Bc4",
              "Bc5", "c3", "dxc3", "Bxf7+", "Kxf7", "Qd5+"),
    start = 8
  ) |>
  add_variation(
    title = "scotch-gambit-variation-london",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Bc4",
              "Bb4+"),
    start = 8
  ) |>
  ## TRAPS
  add_game(
    title = "traps-classical",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5", "Be3"),
    start = 7,
    variations = c("traps-classical-1", "traps-classical-2")
  ) |>
  add_variation(
    title = "traps-classical-1",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5", "Be3",
              "Nf6", "Nxc6", "dxc6", "Qxd8+", "Kxd8", "Bxc5", "Nxe4"),
    start = 10
  ) |>
  add_variation(
    title = "traps-classical-2",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "exd4", "Nxd4", "Bc5", "Be3",
              "d6", "Nxc6", "bxc6", "Bxc5", "dxc5", "Qxd8+", "Kxd8"),
    start = 10
  ) |>
  add_game(
    title = "traps-3d6",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "d6", "dxe5", "dxe5", "Qxd8+"),
    start = 6,
    variations = c("traps-3d6-5Kxd8", "traps-3d6-5Nxd8")
  ) |>
  add_variation(
    title = "traps-3d6-5Kxd8",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "d6", "dxe5", "dxe5", "Qxd8+",
              "Kxd8", "Bc4"),
    start = 10
  ) |>
  add_variation(
    title = "traps-3d6-5Nxd8",
    moves = c("e4", "e5", "Nf3", "Nc6", "d4", "d6", "dxe5", "dxe5", "Qxd8+",
              "Nxd8", "Nxe5"),
    start = 10,
  ) |>
  clean_chess_df() |>
  write_png("Scotch")

ojs_define(scotch_t = scotch)
```

```{ojs}
scotch = transpose(scotch_t)
```

```{ojs}
scotch.filter(d => d.type === 'main')
  .map(d => board_setup(scotch, d.title))
```

## Introduction

```{r}
#| output: asis
put_board("intro")
```

## Main Line (4.Nxd4)

### Classical Variation (4...Bc5) 

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("classical")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* After 4.Nxd4 Bc5 there are three main lines: 
  * <span class="variation" id = "classical-5Be3-7Bc4-O-O"> 5.Be3 </span> (the most popular response)
    * Note: 8...Bb6 is protecting the bishop
    * Instead of 7...O-O, <span class="variation" id = "classical-5Be3-7Bc4-Ne5"> 7...Ne5 </span> is also possible
  * <span class="variation" id = "classical-5Nb3"> 5.Nb3 </span> and <span class="variation" id = "classical-5Nxc6"> 5.Nxc6 </span>

:::

::::

### Schmidt Variation (4...Nf6) 

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("Schmidt")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* After 4.Nxd4 Nf6 there are two options:
  * The Mieses Variation: <span class="variation" id = "Mieses"> 5.Nxc6 </span>
  * The Scotch Four Knights Game: <span class="variation" id = "four-knights"> 5.Nc3 Bb4 </span> 
  or <span class="variation" id = "four-knights-5Nc3-Bc5"> 5...Bc5 </span> 

:::

::::

### Lolli Variation (4...Nxd4?)
The response to 4...Nxd4 is 5.Qxd4, black cannot attack the queen. Any attempt results in a poor position:

::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("Knight-takes")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
* <span class="variation" id = "Knight-takes-Nf6-Nh5"> 5...Nf6 6.e5 </span>, threatens to trap the knight
  * <span class="variation" id = "Knight-takes-Nf6-c5"> 6...c5 </span> is black's best option (still bad)
  * <span class="variation" id = "Knight-takes-Nf6-Ng8"> 6...Ng8 </span> also saves the knight at a severe cost
* <span class="variation" id = "Knight-takes-c5-d5"> 5...c5 6.Qd3 d5 </span> loses the d pawn
  * <span class="variation" id = "Knight-takes-c5-d6"> 6...d6 </span> postpones the loss, but after O-O-O and e4-e5 it will fall
* <span class="variation" id = "Knight-takes-Qf6"> 5...Qf6 </span> leads to a poor position
  * <span class="variation" id = "Knight-takes-Qf6-8f6"> 8...f6 </span> loses a pawn
  * <span class="variation" id = "Knight-takes-Qf6-9Bxd6"> 9...Bxd6 </span> also loses a pawn

:::

::::

### Other fourth moves for black
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("Other-4")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
* Black has a few other options, besides 4...Bc5 and 4...Nf6:
  * <span class="variation" id = "Other-4Nxd4-Qf6"> 4...Qf6 </span> typically transposes into the mainline
  * <span class="variation" id = "Other-4Nxd4-Qh4"> 4...Qh4 </span> (the dubious Steinitz Variation)
  * <span class="variation" id = "Other-4Nxd4-Bb4"> 4...Bb4 </span> again, black has to retreat 6...Bb6
:::

::::

## Scotch Gambit (4.Bc4)
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("scotch-gambit")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}
* Black can accept with <span class="variation" id = "scotch-gambit-variation-accepted"> 4...Bc5 5.c3 dxc3 </span>.
  * Alternatively, <span class="variation" id="scotch-gambit-variation-italian">  5...Nf6 </span> transitions into the Italian Game
* <span class="variation" id = "scotch-gambit-variation-london"> 4...Bb4+ </span> is the London Defense 
:::

::::


## Traps

### Classical Variation (4.Nxd4 Bc5) 
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("traps-classical")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* If black doesn't defend the bishop on c5 after 4.Nxd5 Bc5 5.Be3, white can take the knight on c6, winning the bishop!
  * For example, <span class="variation" id = "traps-classical-1"> 5....Nf6 </span> loses the bishop
  * <span class="variation" id = "traps-classical-2"> 5....d6 </span> defends the bishop, but it's not pretty
  
:::

::::



### 3...d6 
::::{.columns}

:::{.column width='45%'}
```{r}
#| output: asis
put_board("traps-3d6")
```
:::

:::{.column width='55%' style='margin-top: 10px; margin-left: 5px'}

* 3...d6 4.dxe5 dxe5 5. Qxd8 is bad for black
  * If <span class="variation" id = "traps-3d6-5Kxd8"> 5...Kxd8 </span>, 
  black loses the ability to castle and possibly the rook on h8
  * But, <span class="variation" id = "traps-3d6-5Nxd8"> 5...Nxd8 </span> loses a pawn
  
:::

::::

## References {.unnumbered}

<button class="btn" style="width: unset;">
<a href="pgn-files/Scotch.pgn" download="Scotch.pgn">
<i class="fa fa-download"></i> Download PGN
</a>
</button>


<!-- todo: -->
<!--   - 3...d6 -->
<!--   - 4...Nxd4 -->
<!--   - Göring Gambit -->





